---
title: "Grants"
pagetitle: "Research Grants — ALERRT Center"
description: "Awarded grants supporting research on active shooter response, officer training, and police decision-making at the ALERRT Center."
page-layout: full
toc: false
include-in-header:
  - text: |
      <link rel="canonical" href="https://huntermartaindale.com/grants.html">
---

```{r setup, include=FALSE}
library(yaml)
library(htmltools)

`%||%` <- function(a, b) if (!is.null(a)) a else b
has_val <- function(x) !is.null(x) && length(x) > 0 && !(is.atomic(x) && length(x) == 1 && is.na(x))

grants <- yaml::read_yaml("data/grants.yaml")
summary_stats <- tryCatch(
  yaml::read_yaml("data/grants_summary.yaml"),
  error = function(e) list(pass_count = 0, pass_total = 0)
)
total_amount <- sum(sapply(grants, function(g) as.numeric(g$amount %||% 0)))
n_grants <- length(grants)

fmt_money <- function(x) {
  if (!has_val(x)) return("")
  paste0("$", formatC(as.numeric(x), format = "d", big.mark = ","))
}
```

This page lists my externally funded research, training, and evaluation grants. For ongoing recurring training awards (the COPS Office Preparing for Active Shooter Situations program), see [my CV](cv.qmd). I am also available for [grant consulting](#grant-consulting).

::: {.scholar-stats}
::: {.grid}
::: {.g-col-6 .stat-item}
<div class="stat-value">`r n_grants`</div>
<div class="stat-label">Funded Grants</div>
:::
::: {.g-col-6 .stat-item}
<div class="stat-value">`r fmt_money(total_amount)`</div>
<div class="stat-label">Total Funding</div>
:::
:::
<div class="scholar-stats-caption">Excludes the recurring COPS Office PASS training awards (Co-PI), which total `r fmt_money(summary_stats$pass_total)` across `r summary_stats$pass_count` awards.</div>
:::

## Awarded Grants

```{r grant-cards}
render_grant <- function(g) {
  role_str <- g$role %||% ""
  if (identical(role_str, "Co-PI") && has_val(g$pi)) {
    role_str <- sprintf("Co-PI (PI: %s)", g$pi)
  }

  meta_parts <- c(
    if (has_val(g$funder)) g$funder else NULL,
    if (nzchar(role_str)) role_str else NULL,
    if (has_val(g$amount)) fmt_money(g$amount) else NULL
  )
  meta_html <- paste(meta_parts, collapse = " &middot; ")

  subaward_html <- ""
  if (has_val(g$prime_institution)) {
    prime_parts <- c()
    if (has_val(g$prime_pi)) {
      prime_parts <- c(prime_parts, sprintf("Prime PI: %s (%s)", g$prime_pi, g$prime_institution))
    } else {
      prime_parts <- c(prime_parts, sprintf("Prime: %s", g$prime_institution))
    }
    if (has_val(g$prime_total)) {
      prime_parts <- c(prime_parts, sprintf("Prime total %s", fmt_money(g$prime_total)))
    }
    subaward_html <- sprintf(
      '<div class="grant-subaward"><span class="grant-subaward-tag">Subaward</span> %s</div>',
      paste(prime_parts, collapse = " &middot; ")
    )
  } else if (has_val(g$notes)) {
    subaward_html <- sprintf('<div class="grant-notes">%s</div>', g$notes)
  }

  award_html <- ""
  if (has_val(g$award_number))
    award_html <- sprintf('<div class="grant-award">Award #%s</div>', g$award_number)

  HTML(sprintf(
    '<div class="pub-card">
  <div class="pub-card-tag">%s</div>
  <div class="pub-card-title">%s</div>
  <div class="pub-card-meta">%s</div>
  %s
  %s
</div>',
    g$year,
    g$title,
    meta_html,
    subaward_html,
    award_html
  ))
}

div(class = "pub-card-grid", tagList(lapply(grants, render_grant)))
```

## Grant Consulting

I work with academic teams, practitioner agencies, and small businesses on competitive federal and foundation proposals, with particular emphasis on policing, active shooter response, and training program evaluation. Typical engagements include:

- **Proposal review and feedback** on framing, design, and evaluation plans before submission
- **Methodology and evaluation design** for training, intervention, and program evaluation grants (NIJ, BJA, COPS Office, FEMA, NSF, NIH, DHS, SBIR/STTR)
- **Co-investigator and consulting roles** on submitted proposals where my background in active shooter research, officer stress and performance, or use of force is a fit
- **Letters of support and advisory roles** for university and agency partners

To discuss a specific opportunity, use the [contact form](contact.qmd) or email directly. Please include the funding announcement, deadline, and a brief description of the project so I can quickly assess fit and availability.
