---
title: "Research"
pagetitle: "Active Shooter & Policing Research"
description: "Peer-reviewed research on active shooter response, officer stress and performance, use of force decision-making, and public opinion of police."
page-layout: full
toc: false
include-in-header:
  - text: |
      <link rel="canonical" href="https://huntermartaindale.com/research.html">
---

My research spans two primary areas: policing (with emphases on officer stress and physiology, use of force and decision making, and public opinion) and active shooter preparedness and response. Use the topic and year filters below to narrow the list. Summaries are written for a general audience. For full abstracts and citation information, use the DOI or PDF links.

```{r setup}
library(yaml)
library(htmltools)

pubs <- yaml::read_yaml("data/publications.yaml")

stats <- tryCatch(
  yaml::read_yaml("data/scholar_stats.yaml"),
  error = function(e) list(total_citations = "--", h_index = "--", i10_index = "--")
)
```

::: {.scholar-stats}
::: {.grid}
::: {.g-col-4 .stat-item}
<div class="stat-value">`r stats$total_citations`</div>
<div class="stat-label">Citations</div>
:::
::: {.g-col-4 .stat-item}
<div class="stat-value">`r stats$h_index`</div>
<div class="stat-label">h-index</div>
:::
::: {.g-col-4 .stat-item}
<div class="stat-value">`r stats$i10_index`</div>
<div class="stat-label">i10-index</div>
:::
:::
<div class="scholar-stats-caption">Google Scholar, updated weekly.</div>
:::

```{r render-helpers}

`%||%` <- function(a, b) if (!is.null(a)) a else b

has_val <- function(x) !is.null(x) && length(x) > 0 && !(is.atomic(x) && length(x) == 1 && is.na(x))

topic_labels <- c(
  "active-shooter"          = "Active Shooter Events",
  "policing-stress"         = "Officer Stress & Performance",
  "policing-decisions"      = "Decision Making & Use of Force",
  "policing-public-opinion" = "Public Opinion & Legitimacy",
  "other"                   = "Other"
)

esc <- function(x) {
  if (is.null(x)) return("")
  x <- as.character(x)
  x <- gsub("&", "&amp;", x, fixed = TRUE)
  x <- gsub("<", "&lt;", x, fixed = TRUE)
  x <- gsub(">", "&gt;", x, fixed = TRUE)
  x <- gsub('"', "&quot;", x, fixed = TRUE)
  x
}

render_pub <- function(pub) {
  links <- character(0)
  if (has_val(pub$doi))
    links <- c(links, sprintf('<a href="https://doi.org/%s">DOI</a>', pub$doi))
  if (has_val(pub$pdf))
    links <- c(links, sprintf('<a href="%s">PDF</a>', pub$pdf))
  if (has_val(pub$preprint))
    links <- c(links, sprintf('<a href="%s">Preprint</a>', pub$preprint))

  authors_str <- paste(unlist(pub$authors), collapse = ", ")
  journal_str <- pub$journal %||% ""
  if (has_val(pub$volume))
    journal_str <- paste0(journal_str, ", ", pub$volume)
  if (has_val(pub$issue))
    journal_str <- paste0(journal_str, "(", pub$issue, ")")
  if (has_val(pub$pages))
    journal_str <- paste0(journal_str, ", ", pub$pages)

  summary_html <- ""
  if (has_val(pub$plain_summary))
    summary_html <- sprintf('<div class="pub-summary">%s</div>', pub$plain_summary)

  citations_html <- ""
  if (has_val(pub$citations) && as.integer(pub$citations) > 0)
    citations_html <- sprintf(
      '<div class="pub-citations">Cited %d times (Google Scholar)</div>',
      as.integer(pub$citations)
    )

  links_html <- ""
  if (length(links) > 0)
    links_html <- sprintf('<div class="pub-links">%s</div>', paste(links, collapse = ""))

  topic_slugs <- if (has_val(pub$topics)) unlist(pub$topics) else character(0)
  topic_attr  <- paste(topic_slugs, collapse = " ")
  topic_tags_html <- ""
  if (length(topic_slugs) > 0) {
    tags <- vapply(topic_slugs, function(s) {
      label <- if (s %in% names(topic_labels)) topic_labels[[s]] else s
      sprintf('<span class="pub-topic-chip">%s</span>', esc(label))
    }, character(1))
    topic_tags_html <- sprintf('<div class="pub-topic-chips">%s</div>', paste(tags, collapse = ""))
  }

  search_text <- tolower(paste(pub$title, authors_str, journal_str, pub$year, sep = " "))

  HTML(sprintf(
    '<div class="pub-entry" data-topics="%s" data-year="%s" data-search="%s">
  %s
  <h3 class="pub-title">%s</h3>
  <div class="pub-authors">%s</div>
  <div class="pub-journal">%s (%s)</div>
  %s
  %s
  %s
</div>',
    esc(topic_attr),
    esc(pub$year),
    esc(search_text),
    topic_tags_html,
    pub$title,
    authors_str,
    journal_str,
    pub$year,
    summary_html,
    links_html,
    citations_html
  ))
}

# Sort all pubs by year descending for the flat list
years_all <- sapply(pubs, function(p) as.integer(p$year))
pubs_sorted <- pubs[order(years_all, decreasing = TRUE)]
unique_years <- sort(unique(years_all), decreasing = TRUE)
```

```{r filter-bar}
year_opts <- c(
  list(tags$option(value = "all", "All Years")),
  lapply(unique_years, function(y) tags$option(value = as.character(y), as.character(y)))
)

topic_pills <- c(
  list(tags$button(class = "topic-pill active", `data-topic` = "all", "All Topics")),
  lapply(names(topic_labels), function(slug) {
    tags$button(class = "topic-pill", `data-topic` = slug, topic_labels[[slug]])
  })
)

div(
  class = "pub-filter",
  do.call(tags$div, c(list(class = "pub-topic-pills"), topic_pills)),
  div(
    class = "pub-filter-row",
    tags$label(`for` = "pub-year-filter", class = "pub-year-label", "Year:"),
    do.call(tags$select, c(
      list(id = "pub-year-filter", class = "pub-year-select", `aria-label` = "Filter by year"),
      year_opts
    )),
    div(
      class = "pub-count",
      `aria-live` = "polite",
      "Showing ",
      tags$span(id = "pub-visible-count", as.character(length(pubs_sorted))),
      sprintf(" of %d publications", length(pubs_sorted))
    )
  )
)
```

```{r render-flat-list}
tagList(lapply(pubs_sorted, render_pub))
```

```{=html}
<script>
(function() {
  const yearSelect = document.getElementById('pub-year-filter');
  const pills      = document.querySelectorAll('.topic-pill');
  const entries    = document.querySelectorAll('.pub-entry');
  const countEl    = document.getElementById('pub-visible-count');

  let activeTopic = 'all';

  function apply() {
    const yr = yearSelect.value;
    let visible = 0;

    entries.forEach(el => {
      const topics = (el.dataset.topics || '').split(/\s+/).filter(Boolean);
      const year   = el.dataset.year || '';

      const topicMatch = activeTopic === 'all' || topics.includes(activeTopic);
      const yearMatch  = yr === 'all' || year === yr;

      if (topicMatch && yearMatch) {
        el.style.display = '';
        visible++;
      } else {
        el.style.display = 'none';
      }
    });

    countEl.textContent = visible;
  }

  yearSelect.addEventListener('change', apply);
  pills.forEach(btn => {
    btn.addEventListener('click', () => {
      pills.forEach(b => b.classList.remove('active'));
      btn.classList.add('active');
      activeTopic = btn.dataset.topic;
      apply();
    });
  });
})();
</script>
```
