---
title: "Research"
toc: true
toc-location: right
toc-title: "Topics"
toc-depth: 2
---

My research spans two primary areas: policing (with emphases on officer stress and physiology, use of force and decision making, and public opinion) and active shooter preparedness and response. Summaries below are written for a general audience. For full abstracts and citation information, use the DOI or PDF links.

```{r setup}
library(yaml)
library(htmltools)

pubs <- yaml::read_yaml("data/publications.yaml")

render_pub <- function(pub) {
  has_val <- function(x) !is.null(x) && length(x) > 0 && !(is.atomic(x) && length(x) == 1 && is.na(x))

  links <- character(0)
  if (has_val(pub$doi))
    links <- c(links, sprintf('<a href="https://doi.org/%s">DOI</a>', pub$doi))
  if (has_val(pub$pdf))
    links <- c(links, sprintf('<a href="%s">PDF</a>', pub$pdf))
  if (has_val(pub$preprint))
    links <- c(links, sprintf('<a href="%s">Preprint</a>', pub$preprint))

  authors_str <- paste(unlist(pub$authors), collapse = ", ")
  journal_str <- pub$journal %||% ""
  if (has_val(pub$volume))
    journal_str <- paste0(journal_str, ", ", pub$volume)
  if (has_val(pub$issue))
    journal_str <- paste0(journal_str, "(", pub$issue, ")")
  if (has_val(pub$pages))
    journal_str <- paste0(journal_str, ", ", pub$pages)

  summary_html <- ""
  if (has_val(pub$plain_summary))
    summary_html <- sprintf('<div class="pub-summary">%s</div>', pub$plain_summary)

  citations_html <- ""
  if (has_val(pub$citations) && as.integer(pub$citations) > 0)
    citations_html <- sprintf(
      '<div class="pub-citations">Cited %d times (Google Scholar)</div>',
      as.integer(pub$citations)
    )

  links_html <- ""
  if (length(links) > 0)
    links_html <- sprintf('<div class="pub-links">%s</div>', paste(links, collapse = ""))

  HTML(sprintf(
    '<div class="pub-entry">
  <div class="pub-title">%s</div>
  <div class="pub-authors">%s</div>
  <div class="pub-journal">%s (%s)</div>
  %s
  %s
  %s
</div>',
    pub$title,
    authors_str,
    journal_str,
    pub$year,
    summary_html,
    links_html,
    citations_html
  ))
}

`%||%` <- function(a, b) if (!is.null(a)) a else b

render_topic <- function(topic_id, pubs) {
  topic_pubs <- Filter(function(p) topic_id %in% p$topics, pubs)
  if (length(topic_pubs) == 0) {
    return(HTML('<p style="color: #a0aec0; font-style: italic; padding: 0.75rem 0; margin: 0;">No publications listed yet.</p>'))
  }
  years <- sapply(topic_pubs, function(p) as.integer(p$year))
  topic_pubs <- topic_pubs[order(years, decreasing = TRUE)]
  tagList(lapply(topic_pubs, render_pub))
}
```

::: {.topic-section}
## Active Shooter Events

```{r}
render_topic("active-shooter", pubs)
```
:::

::: {.topic-section}
## Policing: Stress, Physiology, and Performance

```{r}
render_topic("policing-stress", pubs)
```
:::

::: {.topic-section}
## Policing: Decision Making and Use of Force

```{r}
render_topic("policing-decisions", pubs)
```
:::

::: {.topic-section}
## Policing: Public Opinion and Legitimacy

```{r}
render_topic("policing-public-opinion", pubs)
```
:::

::: {.topic-section}
## Other Publications

```{r}
render_topic("other", pubs)
```
:::
